Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity

### 2021-03-04 manuscript/supplements_rsfmri.Rmd
includes imputed baseline BMI for one participant

---
title: "Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity"
author:
- Hannah Sophie Heinrichs* [1]
- Frauke Beyer* [1][2]
- Evelyn Medawar [1]
- Kristin Prehn [3][4]
- Jürgen Ordemann [8][9]
- Agnes Floel [5][6][7]
- A. Veronica Witte [1][2][10]
date: 1 Max-Planck-Institute for Human Cognitive and Brain Sciences, Leipzig \newline
  2 CRC 1052 "Obesity Mechanisms", Subproject A1, University of Leipzig \newline 3 Department of Neurology and NeuroCure Clinical Research Center, Charité University Medicine, Berlin \newline 4 Department of Psychology, Medical School Hamburg, Hamburg \newline 5 Department of Neurology, University of Greifswald, Greifswald \newline 6 German Center for Neurodegenerative Diseases, Standort Rostock/Greifswald, Greifswald \newline 7 Center for Stroke Research, Charité University Medicine, Berlin \newline 8 Center for Bariatric and Metabolic Surgery, Charité University Medicine, Berlin \newline 9 Zentrum für Adipositas und Metabolische Chirurgie, Vivantes Klinikum Spandau, Berlin \newline 10 Day Clinic for Cognitive Neurology, University Clinic Leipzig
output:
  bookdown::pdf_book:
    fig_caption: yes
    always_allow_html: true
    number_sections: yes
    toc: no
    extra_dependencies: "subfig"
bibliography: "bibliography.bib"
editor_options:
  chunk_output_type: console
---

@@

@@

## Interaction effect group by time on aggregated FC (preregistered analysis)
```{r load agg FC data and prepare, echo=FALSE}
final_FC <- read.csv("../report/final_FC.csv")
```

### Aggregated DMN for two timepoints, adjusted for age and sex (Model 1a)
```{r calc DMN two tp, age and sex,results = 'asis', echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + Age_BL + Sex + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvDMN2tp=anova(R1,R0)
```

```{r qa check DMN model age,sex, eval=FALSE}
diag=diagnostics.plot(R0)
randefplot=ranef.diagn.plot(R0)

test_vif=lm(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex, data=final_FC)
vif_res=vif(test_vif)
```

```{r DMN2tp results age, sex, caption="DMN connectivity compared bl to fu, adjusted for age and sex", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  custom.model.names = c("R0", "R1"),
  float.pos = "h",
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Group BARS",
    "Age",
    "Sex",
    "Timepoint x Group"
  ),
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = FALSE
)
```

### Aggregated DMN for two timepoints, adjusted for age, sex, mean FD (Model 1b)

```{r calc DMN two tp, age and sex and mFD,results = 'asis', echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + Age_BL + Sex + logmFD + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex + logmFD + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvDMN2tp=anova(R1,R0)
```

```{r qa check DMN model age,sex, mFD, eval=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

```{r DMN2tp results age sex mFD, caption="DMN connectivity compared bl to fu, adjusted for age, sex and mFD", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  custom.model.names = c("R0", "R1"),
  float.pos = "h",
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Group BARS",
    "Age",
    "Sex",
    "logmFD",
    "Timepoint x Group"
  ),
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = FALSE
)
```

### Aggregated DMN for three timepoints, adjusted for age, sex, mean FD (Model 1b)
```{r calc DMN three tp, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + Age_BL + Sex + logmFD +(1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex + logmFD +(1|subj.ID), data=final_FC)
anvDMN3tp=anova(R1,R0)
```

```{r DMN3tp results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  reorder.coef = c(1, 2, 3, 4, 8, 9, 5, 6, 7),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Timepoint FU2",
    "Group BARS",
    "Age",
    "Sex",
    "logmFD",
    "Timepoint FU x Group",
    "Timepoint FU2 x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = FALSE
)
```

### Reward network for two time points, adjusted for age and sex (Model 1a)
```{r calc rew two tp, age, sex, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +  (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvRew2tp=anova(R1,R0)
```
```{r qa check Rew model age,sex, eval=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

@@

```{r Rew2tp results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Group BARS",
    "Age",
    "Sex",
    "Timepoint x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = FALSE
)
```

### Reward network for two timepoints, adjusted for age, sex, mean FD (Model 1b)
```{r calc rew two tp adjusted, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + logmFD +(1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +logmFD +(1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvRew2tpadj=anova(R1,R0)
```

@@

```{r Rew2tpadj results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  reorder.coef = c(1, 2, 3, 7, 4, 5, 6),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Group BARS",
    "Age",
    "Sex",
    "logmFD",
    "Timepoint x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = FALSE
)
```

### Reward network for three timepoints, adjusted for age, sex, mean FD (Model 1b)
```{r calc rew three tp, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + logmFD +(1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +logmFD +(1|subj.ID), data=final_FC)
anvRew3tp=anova(R1,R0)
```
```{r Rew3tp results, caption="DMN connectivity compared bl to fu", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  reorder.coef = c(1, 2, 3, 4, 8, 9, 5, 6, 7),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Timepoint FU2",
    "Group BARS",
    "Age",
    "Sex",
    "logmFD",
    "Timepoint FU x Group",
    "Timepoint FU2 x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = FALSE
)
```
```{r Rew conn over three timepoints, echo=FALSE}
fig_Rewconn <- readRDS(file = "../report/fig/figRewconn.rds")
fig_Rewconn
```

## Effects of average and change BMI on FC
### DMN
#### Model 2a and 2b (adjusting for mFD)
```{r "DMN model, mean, change BMI", eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~  mean.BMI + within.BMI + Age_BL + Sex  + (1|subj.ID), data=final_FC)
R01 = lme4::lmer(mean_DMN_conn ~ mean.BMI +  Age_BL + Sex +(1|subj.ID), data=final_FC)
R02 = lme4::lmer(mean_DMN_conn ~ within.BMI +  Age_BL + Sex +(1|subj.ID), data=final_FC)
anvwithinBMI=anova(R1,R01)
anvmeanBMI=anova(R1,R02)
p_meanBMI=anvmeanBMI$`Pr(>Chisq)`[2]

>>>>

---
title: "Supplementary Material for Effects of bariatric surgery and weight loss on resting state functional connectivity"
author:
- Hannah Sophie Heinrichs* [1]
- Frauke Beyer* [1][2]
- Evelyn Medawar [1]
- Kristin Prehn [3][4]
- Jürgen Ordemann [8][9]
- Agnes Floel [5][6][7]
- A. Veronica Witte [1][2][10]
date: 1 Max-Planck-Institute for Human Cognitive and Brain Sciences, Leipzig \newline
  2 CRC 1052 "Obesity Mechanisms", Subproject A1, University of Leipzig \newline 3 Department of Neurology and NeuroCure Clinical Research Center, Charité University Medicine, Berlin \newline 4 Department of Psychology, Medical School Hamburg, Hamburg \newline 5 Department of Neurology, University of Greifswald, Greifswald \newline 6 German Center for Neurodegenerative Diseases, Standort Rostock/Greifswald, Greifswald \newline 7 Center for Stroke Research, Charité University Medicine, Berlin \newline 8 Center for Bariatric and Metabolic Surgery, Charité University Medicine, Berlin \newline 9 Zentrum für Adipositas und Metabolische Chirurgie, Vivantes Klinikum Spandau, Berlin \newline 10 Day Clinic for Cognitive Neurology, University Clinic Leipzig
output:
  bookdown::pdf_book:
    fig_caption: yes
    always_allow_html: true
    number_sections: yes
    toc: no
    extra_dependencies: ["float","subfig"]
bibliography: "bibliography.bib"
editor_options:
  chunk_output_type: console
---

@@

## Quality Control

## Networks
Figure \@ref(fig:figNetworks) shows the DMN and reward network average maps which we used for extracting aggregated FC values. Both networks included the typically described brain regions (i.e. medial prefrontal cortex, parietal lobules and posterior hippocampus for the DMN, and anterior cingulate, right amygdala and ventromedial-prefrontal cortex for the reward network).
Yet, the reward network was less pronounced (overall lower T-values) and less symmetric (no significant connectivity with left amygdala), which might be due to lower SNR in the seeded brain region (see \@ref(fig:figtSNR)).
Unthresholded maps for the t-tests of the DMN and reward network (which were used for data aggregation) are on Neurovault.
```{r figNetworks, echo=FALSE, out.width="50%", out.height="30%", fig.cap="Resting state networks based on AROMA+CC+GSR input data, one-sample t-tests adjusting for age and sex over all time points and participants with bootstrapped clusterwise inference (FWE-corrected $p < 0.05$)", fig.subcap = c("DMN seeded from precuneus", "Reward network seeded from Nucleus Accumbens", "tSNR differences between regions"),fig.show='hold',fig.align='center'}

networks = c("../report/fig/DMN_thresholded_for_clusterFWE005.pdf",
             "../report/fig/Rew_thresholded_for_clusterFWE005.pdf")
knitr::include_graphics(networks)
```

@@

## Aggregated FC: confirmatory analysis of an interaction effect of group and time 
```{r load agg FC data and prepare, echo=FALSE}
final_FC <- read.csv("../report/final_FC.csv")
final_FC$group_factor=relevel(final_FC$group_factor, "KG")
final_FC=merge(final_FC,subset(final_FC, tp=="bl",select=c("subj.ID", "BMI")), by='subj.ID')
colnames(final_FC)[27]="BMI.bl"
```

```{r identify outliers in these plots, eval=FALSE}
### SUMMARY: all in all there is no reason to exclude the subjects with outlying values in mean Rew/DMN connectivity
final_FC[final_FC$mean_DMN_conn< 0.1, c("mean_DMN_conn", "mean_Rew_conn", "subj.ID_tp", "subj.ID", "tp", "condition")]
#ADI003_fu2 & ADI041_fu -> do not have particularly high head motion
#plot(final_FC$mean_DMN_conn, final_FC$logmFD) -> see two left points
#carpet plots look ok, brain maps of DMN look okish, though not pronounced
#ADI003_fu2 & ADI041 fu: FS issues (Final_score:3, corrected)
qa_info=read.csv("/data/p_02161/ADI_studie/metadata/final_sample_MRI_QA_info.csv")
qa_info[qa_info$subj.ID=="ADI003"&qa_info$tp=="fu2",]
qa_info[qa_info$subj.ID=="ADI041"&qa_info$tp=="fu",]

final_FC[final_FC$mean_Rew_conn>0.3, c("mean_Rew_conn", "subj.ID_tp", "subj.ID", "tp", "condition")]
plot(final_FC$mean_Rew_conn, final_FC$logmFD)
#-> do not have particularly high head motion (two right points)
#ADI069_bl
#nifti looks ok, carpet plot shows lot of stripes.
qa_info[qa_info$subj.ID=="ADI069"&qa_info$tp=="bl",]
#FS issues, parts of skull included
#ADI111_fu2
#nifti looks ok, some residual carpet plot noise
qa_info[qa_info$subj.ID=="ADI111"&qa_info$tp=="fu2",]
#no FS issues
```

### Reward network 
#### Two time points, without adjustments (Model CA1)

<b>

```{r calc rew two tp, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor +  (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvRew2tp=anova(R1,R0)
```

```{r qa check Rew model age,sex, eval=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

@@

```{r Rew2tp results, caption="Interaction of group and time on reward network connectivity for two time points", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Group BARS",
    "Timepoint x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h!",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = TRUE
)
```

#### Two timepoints, adjusted for age, sex and average mFD (Model CA2)

```{r calc rew two tp adjusted 2, fig.cap="Two timepoints, adjusted for age, sex and average mFD (Model CA2)", eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +(1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvRew2tpadj=anova(R1,R0)
```

@@

```{r Rew2tpadj2 results, caption="Interaction of group and time on reward network connectivity for two time points, adjusted for age, sex and average of mFD", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  reorder.coef = c(1, 2, 3, 7, 4, 5, 6),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Group BARS",
    "Age",
    "Sex",
    "av mFD",
    "Timepoint x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h!",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = TRUE
)
```

#### Two timepoints, adjusted for age, sex, average of mFD and baseline BMI (Model CA3)

```{r calc rew two tp adjusted 3, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + BMI.bl + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +BMI.bl + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvRew2tpadj=anova(R1,R0)
```

```{r qa check Rew model age,sex,mFD,baselineBMI,eval=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

test_vif=lm(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +  BMI.bl, data=final_FC)
vif_res=vif(test_vif)
```

```{r Rew2tpadj3 results, caption="Interaction of group and time on reward network connectivity for two time points, adjusted for age, sex, average of mFD and baseline BMI", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  reorder.coef = c(1, 2, 3, 8, 4, 5, 6,7),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Group BARS",
    "Age",
    "Sex",
    "av mFD",
    "baseline BMI",
    "Timepoint x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h!",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = TRUE
)
```

#### Three time points, without adjustments (Model CA1)

```{r calc rew three tp, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + (1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor +  (1|subj.ID), data=final_FC)
anvRew2tp=anova(R1,R0)
```
```{r qa check Rew model age,sex three timepoints, eval=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

```{r Rew3tp results, caption="Interaction of group and time on reward network connectivity for two time points", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Timepoint FU2",
    "Group BARS",
    "Timepoint FU x Group", 
    "Timepoint FU2 x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h!",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = TRUE
)
```

#### Three timepoints, adjusted for age, sex and average mFD (Model CA2)

```{r calc rew three tp adjusted 2, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + (1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +(1|subj.ID), data=final_FC)
anvRew2tpadj=anova(R1,R0)
```

```{r qa check Rew model age,sex,mFD, three timepoints,eval=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

```{r Rew3tpadj 2 results, caption="Interaction of group and time on reward network connectivity for two time points, adjusted for age, sex and average of mFD", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  reorder.coef = c(1, 2, 3, 4, 8, 9, 5, 6, 7),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Timepoint FU2",
    "Group BARS",
    "Age",
    "Sex",
    "av mFD",
    "Timepoint FU x Group", 
    "Timepoint FU2 x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h!",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = TRUE
)
```

#### Three timepoints, adjusted for age, sex, average of mFD and baseline BMI (Model CA3)

```{r calc rew three tp adjusted 3, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + BMI.bl + (1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +BMI.bl + (1|subj.ID), data=final_FC)
anvRew2tpadj=anova(R1,R0)
```

```{r qa check Rew model age,sex,mFD,baselineBMI, three timepoints,eval=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

test_vif=lm(mean_Rew_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +  BMI.bl, data=final_FC)
vif_res=vif(test_vif)
```

```{r Rew3tpadj 3 results, caption="Interaction of group and time on reward network connectivity for two time points, adjusted for age, sex, average of mFD and baseline BMI", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  reorder.coef = c(1, 2, 3, 4,9,10, 5, 6, 7,8),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Timepoint FU2",
    "Group BARS",
    "Age",
    "Sex",
    "av mFD",
    "baseline BMI",
    "Timepoint FU x Group", 
    "Timepoint FU2 x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h!",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = TRUE
)
```

```{r Rew conn over three timepoints, echo=FALSE}
fig_Rewconn <- readRDS(file = "../report/fig/figRewconn.rds")
fig_Rewconn
```

### DMN 
#### Two time points, without adjustments (Model CA1)

```{r calc rew two tp DMN, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor +  (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvDMN2tp=anova(R1,R0)
```
```{r qa check DMN model age,sex, eval=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

```{r DMN2tp results, caption="Interaction of group and time on DMN connectivity for two time points", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Group BARS",
    "Timepoint x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h!",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = TRUE
)
```

#### Two timepoints, adjusted for age, sex and average mFD (Model CA2)

```{r calc DMN two tp adjusted 2, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +(1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvDMN2tpadj=anova(R1,R0)
```

```{r qa check DMN model age,sex,mFD,eval=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

```{r DMN2tpadj2 results, caption="Interaction of group and time on DMN connectivity for two time points, adjusted for age, sex and average of mFD", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  reorder.coef = c(1, 2, 3, 7, 4, 5, 6),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Group BARS",
    "Age",
    "Sex",
    "av mFD",
    "Timepoint x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h!",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = TRUE
)
```

#### Two timepoints, adjusted for age, sex, average of mFD and baseline BMI (Model CA3)

```{r calc DMN two tp adjusted 3, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + BMI.bl + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +BMI.bl + (1|subj.ID), data=final_FC[final_FC$tp!="fu2",])
anvDMN2tpadj=anova(R1,R0)
```

```{r qa check DMN model age,sex,mFD,baselineBMI,eval=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

test_vif=lm(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +  BMI.bl, data=final_FC)
vif_res=vif(test_vif)
```

```{r DMN2tpadj3 results, caption="Interaction of group and time on DMN connectivity for two time points, adjusted for age, sex, average of mFD and baseline BMI", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  reorder.coef = c(1, 2, 3, 8, 4, 5, 6,7),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Group BARS",
    "Age",
    "Sex",
    "av mFD",
    "baseline BMI",
    "Timepoint x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h!",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = TRUE
)
```

#### Three time points, without adjustments (Model CA1)

```{r calc DMN three tp, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + (1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor +  (1|subj.ID), data=final_FC)
anvDMN3tp=anova(R1,R0)
```
```{r qa check DMN model age,sex three timepoints, eval=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

```{r DMN3tp results, caption="Interaction of group and time on DMN connectivity for two time points", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Timepoint FU2",
    "Group BARS",
    "Timepoint FU x Group", 
    "Timepoint FU2 x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h!",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = TRUE
)
```

#### Three timepoints, adjusted for age, sex and average mFD (Model CA2)

```{r calc DMN three tp adjusted 2, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + (1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +(1|subj.ID), data=final_FC)
anvDMN3tpadj=anova(R1,R0)
```

```{r qa check DMN model age,sex,mFD, three timepoints,eval=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

```{r DMN3tpadj 2 results, caption="Interaction of group and time on DMN connectivity for two time points, adjusted for age, sex and average of mFD", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  reorder.coef = c(1, 2, 3, 4, 8, 9, 5, 6, 7),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Timepoint FU2",
    "Group BARS",
    "Age",
    "Sex",
    "av mFD",
    "Timepoint FU x Group", 
    "Timepoint FU2 x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h!",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = TRUE
)
```

#### Three timepoints, adjusted for age, sex, average of mFD and baseline BMI (Model CA3)
```{r calc DMN three tp adjusted 3, eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_DMN_conn ~ tp*group_factor + Age_BL + Sex + mean.logmFD + BMI.bl + (1|subj.ID), data=final_FC)
R0 = lme4::lmer(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +BMI.bl + (1|subj.ID), data=final_FC)
anvDMN3tpadj=anova(R1,R0)
```

```{r qa check DMN model age,sex,mFD,baselineBMI, three timepoints,eval=FALSE}
diagnostics.plot(R0)
ranef.diagn.plot(R0)

test_vif=lm(mean_DMN_conn ~ tp + group_factor + Age_BL + Sex +mean.logmFD +  BMI.bl, data=final_FC)
vif_res=vif(test_vif)
```

```{r DMN3tpadj 3 results, caption="Interaction of group and time on DMN connectivity for two time points, adjusted for age, sex, average of mFD and baseline BMI", results="asis", echo=FALSE}
#tab_model(R1,R0)
texreg(
  list(R0, R1),
  reorder.coef = c(1, 2, 3, 4, 9, 10, 5, 6, 7,8),
  custom.coef.names = c(
    "Intercept (BL, NBARS)",
    "Timepoint FU",
    "Timepoint FU2",
    "Group BARS",
    "Age",
    "Sex",
    "av mFD",
    "baseline BMI",
    "Timepoint FU x Group", 
    "Timepoint FU2 x Group"
  ),
  custom.model.names = c("R0", "R1"),
  float.pos = "h!",
  center = TRUE,
  digits = 3,
  leading.zero = FALSE,
  single.row = TRUE,
  include.adjrs = FALSE,
  include.bic = FALSE,
  table = FALSE,
  use.packages = TRUE
)
```

## Exploratory Analyses: Effects of average and change BMI on FC
### Reward network
#### Model 2.1 and 2.2 (adjusting for mFD)
```{r "reward model, mean, change BMI", eval = TRUE, echo = FALSE}
R1 = lme4::lmer(mean_Rew_conn ~  mean.BMI + within.BMI + Age_BL + Sex  + (1|subj.ID), data=final_FC)
R01 = lme4::lmer(mean_Rew_conn ~ mean.BMI +  Age_BL + Sex +(1|subj.ID), data=final_FC)
R02 = lme4::lmer(mean_Rew_conn ~ within.BMI +  Age_BL + Sex +(1|subj.ID), data=final_FC)
anvwithinBMI=anova(R1,R01)
anvmeanBMI=anova(R1,R02)
p_meanBMI=anvmeanBMI$`Pr(>Chisq)`[2]

R11 = lme4::lmer(mean_Rew_conn ~  mean.BMI + within.BMI + Age_BL + Sex + logmFD + (1|subj.ID), data=final_FC)
R12a = lme4::lmer(mean_Rew_conn ~ within.BMI +  Age_BL + Sex + logmFD+(1|subj.ID), data=final_FC)
anvmeanBMI_adjmFD=anova(R11,R12a)
```
